\documentclass[a4paper]{article}
\usepackage{graphicx, lmodern, geometry, xcolor, enumitem, booktabs, todonotes}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[british]{babel}
\usepackage{mathtools, amsopn, amssymb, amsfonts, amsthm}
\usepackage{hyperref}

\geometry{top=2cm, bottom=2cm, width=17cm}
\setlength{\parindent}{4mm}

\setlist{noitemsep} % no extra space between items
\setlist[enumerate,1]{label = \roman*),ref = \roman*}

\hypersetup{
    breaklinks = {true}, % breaks links over lines
    pdftitle = {BSD Video script},
    pdfauthor = {Christian Wuthrich}
}

\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\ZZ}{\mathbb{Z}}


\begin{document}
  \title{Script for the BSD Video}
  \author{cw}
  \maketitle

\section{Elliptic Curves}
\subsection{Te will explain BSD}

\begin{enumerate}
  \item st+te centred on background
  \item st: I have heard about the Riemann hypothesis (bubbles with $\zeta(s)$)
  You are a number theorist. Are you working on this?
  \item te: Not directly. My research concerns another important conjecture,
  also worth a million dollars (bubble $\zeta(s)$ is kicked out for an elliptic curve)
  \item st: What is it?
  \item te: The Birch and Swinnerton-Dyer conjecture.
  \item st: Can you explain?
  \item te: Sure. (Bubble increases, characters stay in the bubble, until the whole screen is in the bubble. Characters also move to the left lower corner.)
\end{enumerate}

\subsection{Define elliptic curves}
 \begin{enumerate}
   \item te: It deals with equations like $y^2=x^3-4x+1$, called elliptic curves (centred).
   \item st: What do they look like?
   \item te: Here (Equation moves up left, picture appears.)
   \item st: What are other examples?
   \item te: We need $y^2=x^3+$ integer $x+$ integers. (Equation and picture show other curves with coefficients framed)
   \item Go through a family of curve whose discriminant switches sign
   \item st: They are all symmetric ? (Back to $E$)
   \item te: Yes as $y$ only appears as an even power ($(-y)^2 = y^2 = \dots$)
 \end{enumerate}

 \section{Rational points on projective curve}
 \subsection{Rational points}
 \begin{enumerate}
   \item st: What you study about them?
   \item te: I count solutions to the equation with both $x$ and $y$ rational. ($x,y\in\QQ$ appears)
   \item st: Hmm, if $x=0$ and $y$ \dots $y=1$ or $y=-1$.
   \item te: Yep. I chose an example with a lot of solutions (Points are highlighted successively, including one really complicated example)
   \item te: Some other elliptic curves have very few.
 \end{enumerate}

 \subsection{Projective curve}
 \begin{enumerate}
   \item te: We can write $x=X/Z$ and $y=Y/Z$ with integers where $Z$ is the least positive common denominator.
   \item (The equation transforms to substitute, move power).
   \item te: Multiply by $Z^3$. (Get to the projective equation $Y^2Z= X^3-4XZ^2+Z^3$)
   \item st: I know this is a projective curve.
   \item te: Indeed. We can now study integer solution $X$, $Y$, $Z$ to this equation instead.
   \item te: But if we, do we get extra solution, like when $Z$ is negative.
   We need to identify solutions when they are just scalar multiples of each other. ($(X,Y,Z) = (-X,-Y,-Z) = (2X,2Y,2Z)$ as $x = \frac{X}{Z} = \frac{-X}{-Z} = \frac{2X}{2Y}$)
   \item te: And we have added accidentality a new point, the one with $Z=0$ and $X=0$ and $Y=1$.
   \item te: To visual it as a point infinitely far away, we should move to see this. (Turn to the 3d Scene, where the usual plane flips down)
   \item st: Wow. (2D flat characters stay in plane)
   \item te: No worries. Now we see the unique point at infinity and -- look -- the horizon is a tangent to our curve.
   \item (Undo the flip back to 2D.)
 \end{enumerate}



\section{Count points}
\subsection{Counting global points}
\begin{enumerate}
  \item te: The conjecture is about counting rational solutions
  \item st: There are only finitely many?
  \item te: No! For some curves like $y^2=x^3-4x-2$ there are only four points. (plot them)
  \item te: But for our example $E$ there are infinitely many solutions.
  \item te: We count them by size of the integers involved.
  \item te: For instance there are 15 solutions with $\lvert X\rvert, \lvert Y\rvert , \lvert Z\rvert <10$ and 27 smaller than $100$. (give definition of $\mathcal{N}(T)$ and a list of values)
  \item st: I see, these are the first solutions we would find if we search for them with a computer
  \item te: Yep. Searching in a box.
\end{enumerate}

\subsection{Counting modulo}
\begin{enumerate}
 \item te: This counting will be compared to counting modulo.
 \item te: We look for integers such that the two sides have the same remainder when dividing by -- say -- 10.
 \item st: You solve $y^2 = x^3-4x+1$ modulo $10$.
 \item te: Ehmm, yes, but also the points at infinity as there might be more than 1.
 (projective equation modulo 10)
 \item te: There are 27 solutions modulo 10 of which 11 are at infinity. (list them)
 \item te: Here we again put equal solutions $(X,Y,Z)$ that were scaled by $3$, $7$ or $9$, the invertible elements in $\ZZ/10\ZZ$.
 \item te: As $U$ increases the number of solutions modulo $U$ grows.
\end{enumerate}

\section{Conjecture}
\subsection{State conjecture}
\begin{enumerate}
  \item te: Recall $\mathcal{N}$ and $\mathcal{M}$ on the right half
  \item te: Pick $U=T!$
  \item st: If $T$ is biiig, $T!$ is huuuuge.
  \item te: Put $\mathcal{N}(T)$ on top of a fraction, and square it.
  \item te: We compare to $\mathcal{M}(T!)$ by putting it in the denominator.
  \item te: Balance with $T!$ on top and consider what happens if $T\to \infty$.
  \item te: This is the conjecture. This converges to a positive real number.
\end{enumerate}

\subsection{Evidence}
\begin{enumerate}
  \item te: Here is a plot for our curve of this fraction up to $1000$. Not clear yet. (Plot to $T$ up to $1000$, then increase.)
  \item st: Does it converge? It seems bounded and well above $0$.
  \item te: We can plot the fraction for a few other curves, including the one that has only finitely many solutions. (plot several curves in one graph, with the previous ones fading)
  \item st: This last one has these strange jumps (highlight them).
  \item te: Well spotted. That is due to a single pair of rational points.
  Here $\mathcal{N}(T)$ jumps from $9$ to $11$ and then to $13$.
  \item te: The thing is $\mathcal{N}(T)$ grows actually slowly.
  \item st: And proving that conjecture wins you a million?
  \item te: Yes, there is one thing I forgot.
  \item st: What?
  \item te: We have to exclude some curves. Those like this, they are singular. (Show family again but highlight singular curve.)
  \item st: What is the graph for those curves? (Show graph)
  \item te: In general, we need to add one condition (Show conjecture with $\Delta \neq 0$.)
\end{enumerate}

% up to here

\section{Rank and original formulation}

\subsection{The rank}
\begin{enumerate}
  \item st: How slow exactly?
  \item te: That part we know very well, in fact.
  \item te: Here is a theroem. (Show $N(T) \sim \log(T)^{r/2}$)
  \item te: This number $r$ is called the rank of $E$.
  \item (Show plots of three curves)
  \item st: We can replace $N(T)^2$ with $\log(T)$ in the conjecture.
  \item te: Yop. (Show new conjecture)
  \item st: Are the graphs now more convincing?
  \item (Show new graphs)
\end{enumerate}

\subsection{History}
\begin{enumerate}
  \item te: That is actually now equivalent to the original first forumulation of the conjecture found by two British mathematicians.
  \item te: Bryan Birch and Peter Swinnerton-Dyer (show pictures)
  \item te: Swinnerton-Dyer was actually workig in Cambridge on one of the first computers
  \item te: They ended up reformulating the conjecture using what we call $L$-functions after André Weil suggested that to them (show weil?)
  \item te: Now the conjecture looks like this (show rank part)
  \item st: What is $L(E,s)$?
  \item te: An analytic function that encodes the number of points modulo $U$ in a more convenient way.
\end{enumerate}

\subsection{End}
\begin{enumerate}
  \item st: \dots and the two conjectures are equivalent.
  \item te: Nah, not actually. The first one given here is better.
  \item te: Our conjecture implies the modern formulation.
  \item te: And even better it implies the version of the Riemann hypothesis for the function $L(E,s)$.
  \item st: Oh, two millions (walking out of the clous again, $\zeta$ and $L$ together.
\end{enumerate}

Write out limit?

\end{document}
